Score-based tests of measurement invariance: Use in practice

### 2013-10-01 frontiers/frontiers.Rnw
Frontiers revisions: o Revised intro o Updated refs.bib and corrected some errors o Added a few extra readmes
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/semtools@270 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\abstract{
In this paper, we consider a family of 
recently-proposed measurement invariance tests that are based on the {\em scores} of a fitted model.  This family can be used to test for measurement invariance
w.r.t.\ a continuous auxiliary variable, without pre-specification of subgroups.
Moreover, the family can be used when one wishes to test for 
measurement invariance w.r.t.\ an ordinal auxiliary variable, yielding test
statistics that are sensitive to violations that are monotonically related to
the ordinal variable (and less sensitive to non-monotonic violations).  The paper is specifically aimed at potential users of the tests who may wish to know (i) how the tests can be employed for their data, and (ii) whether the tests can accurately identify measurement invariance violations in the presence of model misspecification.  After providing an overview of the tests, we illustrate their general use via the R packages lavaan and strucchange.  We then describe two novel simulations that provide evidence of the tests' practical abilities.  As a whole, the paper provides researchers with the tools and knowledge needed to apply these tests to general measurement invariance scenarios.}

@@

Parameter invariance is a fundamental assumption for measurement model in 
developing psychometric scales. Violation of it could happen in any degree. 
Generally, researchers want to ignore minor violation parameters, e.g. random 
normally distributed deviations from a parameter value across groups. BSEM
(Bayesian Structural Equation Modelling) is proposed not to pick up this kind of 
violating parameters but only "real" violating ones by assigning priors instead of strictly 
constraining equality across groups. After identifying the violation parameters, 
those non-invariant parameters are freely estimated to ensure final correct estimation.

Instead of using this two-step Bayesian analysis procedure, we are applying a family of tests derived
from stochastic process. These tests have been recently proposed to identify specific parameters impacted by measurement invariance. However, they have only been used to a limited type of parameter violation. It is this paper's intent to provide a detailed examination 
of the tests' performance under practical research scenarios. Specifically, we will examine these tests
specificity in identifying the violation parameter without giving false positive results. Moreover, in practice model misspecification is an inevitable issue to a certain extent, we will demonstrate these tests
results under model misspecification condition. 
\seeme{What about this intro? too much BSEM?}
%In order to fix the psychometric scale, we need to specify the violating parameter.  
%Moreover, in practice model misspecification is an inevitable issue to a certain extent 
%and may interfere with parameter invariance specificity. A family of tests derived from 
%stochastic process has been recently proposed to identify specific parameters impacted 
%by measurement invariance violation. However, these tests have only been used to a limited 
%type of parameter violation. It is this paper's intent to provide a detailed examination 
%of the tests' performance under practical research scenarios.

In the following section, we first briefly review the 
theoretical framework of proposed statistical tests and
provide a short tutorial illustrating the use of the tests in R.
Next, we study the tests'
ability through simulations that mimic practical research. 
Finally, some suggestion on the tests' use in practice is provided.

@@

\begin{eqnarray}
    \label{eq:dmax}
    \mathit{DM} & = & \max_{i = 1,\dots, n} \max_{j = 1, \dots, k} | {\bm B}(\hat {\bm \theta})_{ij} \\
        \label{eq:cvm}
    \mathit{CvM}     & = & n^{-1} \sum_{i = 1,\dots, n} \sum_{j = 1, \dots, k} {\bm B}(\hat {\bm \theta})_{ij}^2, \\
    \label{eq:maxlm}
    \max \mathit{LM} & = & \max_{i = \underline{i}, \dots, \overline{\imath}} ~
      \left\{ \frac{i}{n} \left( 1 - \frac{i}{n} \right) \right\}^{-1}
      \sum_{j = 1, \dots, k} {\bm B}(\hat {\bm \theta})_{ij}^2.
\end{eqnarray}

@@

## remove cases with imputed values(not in 1,...,9)
compcases <- apply(YouthGratitude[,4:28], 1, function(x) all(x %in% 1:9))
yg <- YouthGratitude[compcases,]
@
Next, we fit two models in lavaan: a one-factor model where loadings are restricted 
to be equal across age groups, and a one-factor model where loadings are free across age groups.
<<modest>>=
## Restricted model
reduced <- cfa("f1 = ~gq6_1 + gq6_2 + gq6_3 + gq6_4 + gq6_5",
             data = yg, group = "agegroup", meanstructure = TRUE,
             group.equal = "loadings")

@@

Another similar statistics is $\mathit{LM}_\mathit{uo}$ as shown in Equation~ \eqref{eq:lmuo}. We can obtain this statistic by using the following function. 
<<LM_UO>>=
## unordered LM
lm_uo <- sctest(reduced, as.numeric(yg$agegroup), parm = 1:4, stat = "LMuo")
round(lm_uo$p.value, 4)
@
The above command specifies that we wish to test model parameter numbers 1 through 4, which are the factor loadings supplied by lavaan.  The ordering of parameters can be obtained via the command \verb+coef(reduced)+.

Because our sample size is large, this likelihood ratio test is known to be sensitive to 
small measurement invariance violations \cite{Ben80}.  That is, the above tests 
are sensitive to small measurement invariance violations that are not likely to be 
of interest to researchers.  For example, imagine that the 15-year-olds' 
parameters are slightly different than the other age groups.  
The 15-year-olds are in the middle of the age groups, and there 
is not likely to be any theoretical justification for 15-year-olds 
differing from every other age group.  One solution to this problem would be the {\em approximate invariance} methods proposed by Muth\'{e}n \cite{muthen13}.
Alternatively, we can use the proposed family of score-based statistics to obtain tests that are sensitive to the ordering of age.

\subsection{Continuous Treatment}
If we are interested in measurement invariance violations that are 
monotonic with the age groups, it is perhaps simplest to treat the 
age groups as continuous.  In doing so, we can use the statistics 
from Equations~\eqref{eq:dmax},~\eqref{eq:cvm}, and~\eqref{eq:maxlm}.  
That is, we can fit a model whose parameters 
are restricted to be equal across all individuals and then examine 
how individuals' scores $s(\hat{\theta};x_{i})$ fluctuate with their
age (where age ties are broken arbitrarily).
This is demonstrated below, with similar code being useful when one is 
testing measurement invariance w.r.t.\ truly continuous variables.

@@

To carry out the tests, we can rely on the same function that we used
for the continuous test statistics.  As mentioned previously,
calculation of the ``maxLMo'' statistic (Equation~\eqref{eq:maxlmo})
can be lengthy from the need to simulate critical values.
%% This is more complicated than necessary, but it is written like
%% this so that we can load the ordinal critical values behind the
%% scenes without confusing the reader.
<<critvals,echo=FALSE,strip.white=all>>=
if(file.exists("opval1.rda")){
  load("opval1.rda")
} else {
  gefp1 <- gefp(reduced, fit = NULL, order.by = as.numeric(yg$agegroup),
                vcov = info_full, sandwich = FALSE, parm = 1:4)
  opval1 <- ordL2BB(gefp1)
  save(opval1, file="opval1.rda")
}
## Get test statistics using fnl=opval1 without showing it in the paper
wdmo <- sctest(reduced, as.numeric(yg$agegroup), parm = 1:4, stat = "WDMo")
maxlmo <- sctest(reduced, as.numeric(yg$agegroup), parm = 1:4, stat = "maxLMo",
                 fnl = opval1)
@ 
<<ordtest,eval=FALSE,strip.white=all>>=
wdmo <- sctest(reduced, as.numeric(yg$agegroup), parm = 1:4, stat = "WDMo")
maxlmo <- sctest(reduced, as.numeric(yg$agegroup), parm = 1:4, stat = "maxLMo")
@ 
<<pval,strip.white=all>>=
round(c(wdmo$p.value, maxlmo$p.value), 2)
@ 
In computing the ordinal test statistics, we
obtain~$p=\Sexpr{round(wdmo$p.value,2)}$
and~$p=\Sexpr{round(maxlmo$p.value,2)}$, respectively.
Both $p$-values are clearly larger than that of the 
likelihood ratio test and neither is significant at $\alpha=0.05$. 
This provides evidence that there is no measurement
invariance violation that is monotonic with age group.  Instead, given
the large sample size, the likelihood ratio test may be overly
sensitive to anomalous, non-monotonic violations at one (or a few) age groups.

@@

In the above sections, we have illustrated the score-based tests'
computation in R.  We suspect that the ordinal tests will be most
popular with users, because measurement invariance tests are typically
carried out across categories (ordered or not), as opposed to
continuous variables.  Thus, in the sections below, we report
novel simulations to study the ordinal statistics' expected behavior
in practice.  In particular, we wish to study (i) the extent to which the
ordinal statistics attribute measurement invariance violations to the
correct parameter(s), and (ii) the extent to which the tests are
robust to model misspecification.

@@

To examine these specificity issues, we generated data from a
two-factor model with three indicators each (see Figure~\ref{fig:path}).
The measurement invariance
violation occurred in one of three places: the factor loading associated with Scale 1 
 ($\lambda_{11}$), the unique variance associated with Scale 1
 ($\epsilon_{11}$), or the factor covariance $\sigma_{12}$.  
We then tested for measurement invariance in seven subsets of parameters: the three
individual parameters noted above, all six factor loadings, % $\lambda_{11}--\lambda_{62}$, and 
and all six unique variances. % $\epsilon_{11}--\epsilon_{66}$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Power and Type I error were examined across three sample sizes
($n=120,480,960$), three numbers of categories ($m=4,8,12$) and
17 magnitudes of invariance violations. 
The measurement invariance violations began at level $1+m/2$ of $V$
and were consistent thereafter. These
violations were based on the auxiliary variable $V$: individuals below
the $1+m/2$ percentile of $V$ deviated from individuals above the $1+m/2$ 
percentile  by $d$ times the parameters' asymptotic standard errors
(scaled by $\sqrt n$), with $d=0,0,25,0.5,...,4$. 
For each combination of sample size ($n$) $\times$ violation
magnitude ($d$) $\times$ violating parameter $\times$ categories $m$, 5000 datasets were
generated and tested. Statistics from Equations~\eqref{eq:wdm}, ~\eqref{eq:maxlmo} and~\eqref{eq:lmuo} were examined. 
In all conditions, we
maintained equal sample sizes at each level of the ordinal variable.

@@

Full simulation results are presented in Figure~\ref{fig:sim11res} to 
Figure~\ref{fig:sim13res}; 
Figure~\ref{fig:sim11res} displays power curves as a function of 
violation magnitude for the first
factor loading $\lambda_{11}$, with panels reflecting the parameters 
being tested and lines reflecting $n$.
Figures~\ref{fig:sim12res} and Figure~\ref{fig:sim13res} display 
similar power curves when the factor covariance 
$\phi_{12}$ and error variance $\epsilon_{11}$ violate measurement
invariance, respectively. 
All three test statistics exhibited 
similar results, with $\max\mathit{LM}_{uo}$ demonstrating lower power across all situations. This statistic 
is asymptotically equivalent to the LRT as what we describe in introduction. $\mathit{WDM}_o$  and $\max \mathit{LM}_o$ exhibited equivalent power curves because, when only one parameter is tested, the statistics are equivalent.

@@

In summary, we found that the proposed tests can attribute
measurement invariance violations to the correct parameter.  This
provides evidence that, in practice, one can have confidence in the
tests' abilities to locate the measurement invariance violation.  Of
course, this statement is qualified by the fact that, in this
simulation, the model was correctly specified.  In the following
simulations, we examine the tests' performance when the model is
misspecified.

@@

\subsection{Results}
Results are presented by the parameter that violated measurement invariance.
Of primary interest is Figure~\ref{fig:sim21res}, which displays results when the unmodeled loading violates 
measurement invariance. One can generally observe that 
tests of the first loading and error variance parameter exhibited high power, reflecting a high Type I error rate.  Tests associated with the factor covariance did not demonstrate this error, however. In terms of specific statistic performance, $\max \mathit{LM}_o$ test and $\mathit{WDM}_o$ test demonstrated higher power than $\mathit{LM}_{uo}$ in each panel, especially with increasing levels. It is indicating ordered statistics is more inclined to pick up the unmodelled parameter violation in the manifest variables' associated loading and error terms. 
\seeme{Is this sentence enough to compare ordered and unordered statistics?}

When the modeled factor loading, $\lambda_{11}$, violated
measurement invariance, the statistics were generally able to pick up the violation despite the misspecification.
A similar pattern of specificity and power were observed when the unique variance and factor covariance parameters violated measurement invariance; the figures associated with these results are shown in the Appendix. Also, the power of ordered statistics $\max \mathit{LM}_o$ test and $\mathit{WDM}_o$ test showed higher power than unordered $\mathit{LM}_{uo}$ in each panel.

In summary, the proposed test statistics appear robust to unmodeled loading parameters,so long
as the umodeled parameter does not violate measurement invariance. If the unmodeled parameter 
dose violate measurement invariance, however, then the tests assign this violation to other 
parameters that do not violate measurement invariance. The impacted parameters include the error
variance and other loadings associated with the manifest variables that had the unmodeled 
loading. Thus, prior to testing measurement invariance, it is important to study the extent to
which the hypothesized model includes all parameters of importance.

@@

In this paper, we first described a novel family of test statistics for measurement invariance and illustrated their use via the R package lavaan. Next, we examined these statistics' ability to specifically pick up the violation parameter and specificity robustness to model specification. We found the proposed statistics could select the modeled parameter violating measurement invariance even though the model is misspecified in general.

In the reminder of the paper, we will first consider the applicability of these tests in exploring the reason of measurement invariance. Next, the extension of these tests to other fit functions and more specialized models will be discussed. 
\seeme{Are these two paragraphs OK?}

@@

\subsection{Extension}
In this paper, We focused on testing for measurement invariance in factor analysis models that assume multivariate normality and that are estimated via ML.  The family of tests described here generally apply to estimation methods that maximize/minimize a fit function, however \cite<see>{zeihor07}, so they are potentially applicable to alternative SEM discrepancy functions such as Weighted Least Squares \cite{bollen98}.  Score calculation for these alternative discrepancy functions has not been implemented (to our knowledge), though the calculation certainly could be implemented.  Test statistic calculation and inference would then proceed in exactly the same manner as the calculation and inference illustrated in this paper.

@@

\subsection{Conclusion}
\readme{Not sure whether we need this paragraph, but I still need to think about it.}
In summary, the ordinal test statistic proposed have relatively-high power for detecting measurement invariance violation parameter specifically that are monotonic with the auxiliary ordinal variable. This
feature is robust as long as the violation parameter is included in the testing model. Furthermore, as illustrated in tutorial part, the use of these tests is convenient without changing the focal psychometric model. In all, the tests have advantageous properties that should be implemented in practice.

@@

This Appendix demonstrated the results for Simulation 2 when there exists model misspecification (lacking one path from Scale 1 to Math). Figure ~\ref{fig:sim22res} to Figure ~\ref{fig:sim24res} showed the violation parameter is first loading $\lambda_{11}$, covariance $\sigma_{12}$ and 
first error term $\psi_{11}$, respectively.

>>>>

\abstract{
In this paper, we consider a family of 
recently-proposed measurement invariance tests that are based on the scores of a fitted model.  This family can be used to test for measurement invariance
w.r.t.\ a continuous auxiliary variable, without pre-specification of subgroups.
Moreover, the family can be used when one wishes to test for 
measurement invariance w.r.t.\ an ordinal auxiliary variable, yielding test
statistics that are sensitive to violations that are monotonically related to
the ordinal variable (and less sensitive to non-monotonic violations).  The paper is specifically aimed at potential users of the tests who may wish to know (i) how the tests can be employed for their data, and (ii) whether the tests can accurately identify measurement invariance violations in the presence of model misspecification.  After providing an overview of the tests, we illustrate their general use via the R packages lavaan and strucchange.  We then describe two novel simulations that provide evidence of the tests' practical abilities.  As a whole, the paper provides researchers with the tools and knowledge needed to apply these tests to general measurement invariance scenarios.}

@@

Many of the papers in this special issue focus on the topic of approximate measurement invariance: we know that strict hypotheses of measurement invariance do not hold exactly across different groups, and this should be reflected in tests of measurement invariance.  BSEM
(Bayesian Structural Equation Modeling) generally handles these ideas by replacing across-group equality constraints with informative prior distributions.  In this paper, we describe an alternative approach: the development of test statistics that are sensitive to invariance violations of interest and insensitive to ``anomalous'' invariance violations.  The test statistics are specifically applicable to situations where one wishes to test for measurement invariance with respect to an ordinal variable, and they are special cases of a family of tests that may generally be used to study measurement invariance w.r.t.\ continuous, categorical, and ordinal variables.

The family of tests described in this paper have recently been studied in the context of measurement invariance \cite{MerZei13,MerFanZei}, though their practical application has been limited to a small set of simulations and datasets.  In this paper, we provide a detailed illustration of the tests' use in practice and a detailed examination 
of the tests' performance under scenarios likely to be encountered in practice. 
%In order to fix the psychometric scale, we need to specify the violating parameter.  
%Moreover, in practice model misspecification is an inevitable issue to a certain extent 
%and may interfere with parameter invariance specificity. A family of tests derived from 
%stochastic process has been recently proposed to identify specific parameters impacted 
%by measurement invariance violation. However, these tests have only been used to a limited 
%type of parameter violation. It is this paper's intent to provide a detailed examination 
%of the tests' performance under practical research scenarios. 
In the following section, we first briefly review the 
theoretical framework of the proposed tests and
provide a short tutorial illustrating the use of the tests in R.
Next, we study the tests' performance in simulations that mimic practical research scenarios. 
Finally, we provide some further discussion on the tests' use in practice.

@@

\begin{eqnarray}
    \label{eq:dmax}
    \mathit{DM} & = & \max_{i = 1,\dots, n} \max_{j = 1, \dots, k} | {\bm B}(\hat {\bm \theta})_{ij} | \\
        \label{eq:cvm}
    \mathit{CvM}     & = & n^{-1} \sum_{i = 1,\dots, n} \sum_{j = 1, \dots, k} {\bm B}(\hat {\bm \theta})_{ij}^2, \\
    \label{eq:maxlm}
    \max \mathit{LM} & = & \max_{i = \underline{i}, \dots, \overline{\imath}} ~
      \left\{ \frac{i}{n} \left( 1 - \frac{i}{n} \right) \right\}^{-1}
      \sum_{j = 1, \dots, k} {\bm B}(\hat {\bm \theta})_{ij}^2.
\end{eqnarray}

@@

## Remove cases with imputed values (not in 1,...,9)
compcases <- apply(YouthGratitude[,4:28], 1, function(x) all(x %in% 1:9))
yg <- YouthGratitude[compcases,]
@
Next, we fit two models in lavaan: a one-factor model where loadings are restricted 
to be equal across age groups, and a one-factor model where loadings are free across age groups.
<<modest>>=
## Restricted model
reduced <- cfa("f1 = ~gq6_1 + gq6_2 + gq6_3 + gq6_4 + gq6_5",
             data = yg, group = "agegroup", meanstructure = TRUE,
             group.equal = "loadings")

@@

To obtain the asymptotically equivalent $\mathit{LM}_\mathit{uo}$ (Equation~\eqref{eq:lmuo}), we can use the following command.
<<LM_UO>>=
## unordered LM
lm_uo <- sctest(reduced, as.numeric(yg$agegroup), parm = 1:4, stat = "LMuo")
round(lm_uo$p.value, 4)
@
This command specifies that we wish to test model parameter numbers 1 through 4, which are the factor loadings supplied by lavaan.  The ordering of parameters can be obtained via the command \verb+coef(reduced)+.

Because our sample size is large, the likelihood ratio test is known to be sensitive to 
small measurement invariance violations \cite{Ben80}.  That is, the above tests 
are sensitive to small measurement invariance violations that are not likely to be 
of interest to researchers.  For example, imagine that the 15-year-olds' 
parameters are slightly different than the other age groups.  
The 15-year-olds are in the middle of the age groups, and there 
is not likely to be any theoretical justification for 15-year-olds 
differing from every other age group.  One solution to this problem would be the {\em approximate invariance} methods proposed by Muth\'{e}n \cite{muthen13}.
Alternatively, we can use the proposed family of score-based statistics to obtain tests that are sensitive to the ordering of age.

\subsection{Continuous Treatment}
If we are interested in measurement invariance violations that are 
monotonic with the age groups, it is perhaps simplest to treat the 
age groups as continuous.  In doing so, we can use the statistics 
from Equations~\eqref{eq:dmax},~\eqref{eq:cvm}, and~\eqref{eq:maxlm}.  
That is, we can fit a model whose parameters 
are restricted to be equal across all individuals and then examine 
how individuals' scores $s(\hat{\theta};x_{i})$ fluctuate with their
age (where age ties are broken arbitrarily).
This is demonstrated below, with similar code being useful when one is 
testing for measurement invariance w.r.t.\ truly continuous variables.

@@

To carry out the tests, we can rely on the same function that we used
for the continuous test statistics.  As mentioned previously,
calculation of the $\max\mathit{LM}_o$ statistic (Equation~\eqref{eq:maxlmo})
can be lengthy from the need to simulate critical values.
%% This is more complicated than necessary, but it is written like
%% this so that we can load the ordinal critical values behind the
%% scenes without confusing the reader.
<<critvals,echo=FALSE,strip.white=all>>=
if(file.exists("opval1.rda")){
  load("opval1.rda")
} else {
  gefp1 <- gefp(reduced, fit = NULL, order.by = as.numeric(yg$agegroup),
                vcov = info_full, sandwich = FALSE, parm = 1:4)
  opval1 <- ordL2BB(gefp1)
  save(opval1, file="opval1.rda")
}
## Get test statistics using fnl=opval1 without showing it in the paper
wdmo <- sctest(reduced, as.numeric(yg$agegroup), parm = 1:4, stat = "WDMo")
maxlmo <- sctest(reduced, as.numeric(yg$agegroup), parm = 1:4, stat = "maxLMo",
                 fnl = opval1)
@ 
<<ordtest,eval=FALSE,strip.white=all>>=
wdmo <- sctest(reduced, as.numeric(yg$agegroup), parm = 1:4, stat = "WDMo")
maxlmo <- sctest(reduced, as.numeric(yg$agegroup), parm = 1:4, stat = "maxLMo")
@ 
<<pval,strip.white=all>>=
round(c(wdmo$p.value, maxlmo$p.value), 2)
@ 
In computing the ordinal test statistics, we
obtain~$p=\Sexpr{round(wdmo$p.value,2)}$
and~$p=\Sexpr{round(maxlmo$p.value,2)}$, respectively.
Both $p$-values are clearly larger than that of the 
likelihood ratio test and neither is significant at $\alpha=0.05$. 
This provides evidence that there is no measurement
invariance violation that is monotonic with age group.  Instead, given
the large sample size, the likelihood ratio test may be overly
sensitive to anomalous, non-monotonic violations at one (or a few) age groups.

@@

In the above sections, we have illustrated the score-based tests'
computation in R.  We suspect that the ordinal tests will be most
popular with users, because measurement invariance tests are typically
carried out across categories (ordered or not), as opposed to
continuous variables.  Thus, in the sections below, we conduct
novel simulations to study the ordinal statistics' expected behavior
in practice.  In particular, we wish to study (i) the extent to which the
ordinal statistics attribute measurement invariance violations to the
correct parameter(s), and (ii) the extent to which the tests are
robust to model misspecification.

@@

To examine these specificity issues, we generated data from a
two-factor model with three indicators each (see Figure~\ref{fig:path}).
The measurement invariance
violation occurred in one of three places: the factor loading associated with Scale 1 
 ($\lambda_{11}$), the unique variance associated with Scale 1
 ($\psi_{11}$), or the factor covariance $\sigma_{12}$.  
\readme{Isn't this five subsets of parameters, not seven?}
 We then tested for measurement invariance in seven subsets of parameters: the three
individual parameters noted above, all six factor loadings, % $\lambda_{11}--\lambda_{62}$, and 
and all six unique variances. % $\epsilon_{11}--\epsilon_{66}$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Power and Type I error were examined across three sample sizes
($n=120,480,960$), three numbers of categories ($m=4,8,12$) and
17 magnitudes of invariance violations. 
The measurement invariance violations began at level $1+m/2$ of $V$
and were consistent thereafter: individuals below
the $1+m/2$ percentile of $V$ deviated from individuals above the $1+m/2$ 
percentile  by $d$ times the parameters' asymptotic standard errors
(scaled by $\sqrt n$), with $d=0,0,25,0.5,...,4$. 
For each combination of sample size ($n$) $\times$ violation
magnitude ($d$) $\times$ violating parameter $\times$ categories $m$, 5000 datasets were
generated and tested. Statistics from Equations~\eqref{eq:wdm}, ~\eqref{eq:maxlmo} and~\eqref{eq:lmuo} were examined. 
In all conditions, we
maintained equal sample sizes at each level of the ordinal variable.

@@

Full simulation results are presented in Figure~\ref{fig:sim11res} to 
Figure~\ref{fig:sim13res}; 
Figure~\ref{fig:sim11res} displays power curves as a function of 
violation magnitude for the first
factor loading $\lambda_{11}$, with panels reflecting the parameters 
being tested and lines reflecting $n$.
Figures~\ref{fig:sim12res} and Figure~\ref{fig:sim13res} display 
similar power curves when the factor covariance 
$\phi_{12}$ and error variance $\epsilon_{11}$ violate measurement
invariance, respectively. 
All three test statistics exhibited 
similar results, with $\max\mathit{LM}_{uo}$ demonstrating lower power across all situations. As described earlier, this statistic 
is asymptotically equivalent to the LRT. $\mathit{WDM}_o$  and $\max \mathit{LM}_o$ exhibited equivalent power curves because, when only one parameter is tested, the statistics are equivalent.

@@

In summary, we found that the proposed tests can attribute
measurement invariance violations to the correct parameter.  This
provides evidence that, in practice, one can have confidence in the
tests' abilities to locate the measurement invariance violation.  Of
course, this statement is qualified by the fact that, in this
simulation, the model was correctly specified.  In the following
simulation, we examine the tests' performance when the model is
misspecified.

@@

\subsection{Results}
Results are presented by the parameter that violated measurement invariance.
Of primary interest is Figure~\ref{fig:sim21res}, which displays results when the unmodeled loading violates 
measurement invariance. One can generally observe that 
tests of the first loading and error variance parameter exhibited high power, reflecting a high Type I error rate.  Tests associated with the factor covariance did not demonstrate this error, however. In terms of specific statistic performance, $\max \mathit{LM}_o$ test and $\mathit{WDM}_o$ test demonstrated higher Type I error than $\mathit{LM}_{uo}$ in each panel, especially with increasing levels.  This is likely because the unmodeled loading's noninvariance was monotonic with $V$; if it were not monotonic, we would expect $\mathit{LM}_{uo}$ to have higher Type I error.

When the modeled factor loading, $\lambda_{11}$, violated
measurement invariance, the statistics were generally able to pick up the violation despite the misspecification.
A similar pattern of specificity and power were observed when the unique variance and factor covariance parameters violated measurement invariance; the figures associated with these results are shown in the Appendix. Also, the power of ordered statistics $\max \mathit{LM}_o$ test and $\mathit{WDM}_o$ test showed higher power than unordered $\mathit{LM}_{uo}$ in each of these panels.

\readme{Make sure there is a space after each comma and period:}
In summary, the proposed test statistics appear robust to unmodeled loading parameters,so long
as the umodeled parameter does not violate measurement invariance. If the unmodeled parameter 
dose violate measurement invariance, however, then the tests assign this violation to other 
parameters that do not violate measurement invariance. The impacted parameters include the error
variance and other loadings associated with the manifest variables that had the unmodeled 
loading. Thus, as it is with other tests of measurement invariance, it is important to study the extent to
which the hypothesized model includes all parameters of importance.

@@

In this paper, we first described a novel family of test statistics for measurement invariance and illustrated their use via the R package lavaan. Next, we examined these statistics' abilities to identify the parameter violating measurement invariance under well-specified and misspecified models. We found the proposed statistics could generally isolate the model parameter violating measurement invariance, so long as the violating parameter is included in the model.

In the reminder of the paper, we will first consider the applicability of these tests as compared to traditional tests. Next, we discuss test extension to other fit functions and to other specialized models.

@@

\subsection{Extension}
In this paper, We focused on testing for measurement invariance in factor analysis models that assume multivariate normality and that are estimated via ML.  The family of tests described here generally apply to estimation methods that maximize/minimize a fit function, however \cite<see>{zeihor07}, so they are potentially applicable to alternative SEM discrepancy functions such as Weighted Least Squares \cite<e.g.,>{broarm95}.  Score calculation for these alternative discrepancy functions has not been implemented (to our knowledge), though the calculation certainly could be implemented.  Test statistic calculation and inference would then proceed in exactly the same manner as the calculation and inference illustrated in this paper.

@@

% Removed for now:
%% \subsection{Conclusion}
%% \readme{Not sure whether we need this paragraph, but I still need to think about it.}
%% In summary, the ordinal test statistic proposed have relatively-high power for detecting measurement invariance violation parameter specifically that are monotonic with the auxiliary ordinal variable. This
%% feature is robust as long as the violation parameter is included in the testing model. Furthermore, as illustrated in tutorial part, the use of these tests is convenient without changing the focal psychometric model. In all, the tests have advantageous properties that should be implemented in practice.

@@

This Appendix includes the results for Simulation 2 when there exists model misspecification (lacking one path from Scale 1 to Math). Figure~\ref{fig:sim22res} to Figure~\ref{fig:sim24res} display results when the loading $\lambda_{11}$, covariance $\sigma_{12}$, and 
error term $\psi_{11}$ violate invariance, respectively.
